Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-15 chapters/LBM_technique.tex
Making notation consistent

Bijels require a multiscale modeling approach to accurately capture the rich array of physical phenomena 
occurring across multiple length and time scales. Within a bijel, one must consider fluid flow, phase separation, particle-fluid coupling, and interparticle 
interactions. The length scales of interest range in the hundreds of nanometer to  tens of micron scale, demanding a model capable of resolving fine structural details while also 
capturing mesoscale dynamics. In the following sections, a comprehensive review of the relevant physical processes is provided, laying the foundation for the 
numerical methods used in this work.

@@

where $\rho$ is the fluid density and $\vec{u}$ is the fluid velocity. Based on the system being modeled, we assume that the fluid is incompressible, reducing the continuity equation to
$\nabla\cdot \vec{u} = 0$ The momentum conservation equation can also be written by applying Newton's second law to the fluid element. This yields the Cauchy momentum equation for an
incompressible fluid, where changes in momentum arise due to pressure gradients, viscous stresses, and body forces. The general form of the momentum equation is given by,

\begin{equation}
    \rho \left(\frac{\partial u_i}{\partial t} + (u_i\cdot\frac{\partial u_i}{x_i}) \right) = \frac{\partial \sigma_{ij}}{\partial x_j} + f_i
\end{equation}

where $f_i$ is the force exerted on the fluid from external forces such as gravity or magnetic interactions and $\sigma_{ij}$ is the stress tensor. For a Newtonian, isotropic fluid, 
the viscous stress tensor is given by

\begin{equation}
    \sigma_{ij} = -p\delta_{ij} + \eta((\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i}) - \frac{2}{3}(\frac{\partial u_j}{\partial x_i})^2\delta_{ij})
\end{equation}

@@

In the single component case, $-\nabla p = \vec{f} = 0$ as there are no external forces like gravity acting on the fluid and there are is no hydrodynamic pressure being applied to the 
fluid resulting in the following form of the incompressible Navier Stokes equation.

\begin{equation}
    \rho \left(\frac{\partial\vec{u}}{\partial t} + (\vec{u}\cdot\nabla)\vec{u} \right) = \eta \nabla^2 \vec{u}
\end{equation}

@@

\begin{equation}
    \bar{l} = \frac{l}{l_0}, \quad \bar{t} = \frac{t}{t_0}, \quad \bar{\rho} = \frac{\rho}{\rho_0}
\end{equation}

@@

\begin{equation}
    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = \frac{1}{Re} \nabla^2 \bar{\vec{u}}
\end{equation}

@@

Bijels form through spinodal decomposition of two partially miscible fluids, a process that can be effectively modeled using the Cahn-Hilliard equation. \cite{cahn_spinodal_1961} While the
original equation is written for a concentration of species $c$. For a binary mixture, it can be recast in terms of a conserved scalar order parameter $\phi$, typically representing the 
local concentration difference between the two fluid components,

\begin{equation}
    \frac{\partial \phi}{\partial t} = \nabla \cdot \left( M \nabla \mu \right)
\end{equation}

Here, $M$ is the mobility coefficient and $\mu$ is the chemical potential, which is derived from the variation of the free energy functional $F[\phi]$ which is the sum of a bulk free energy
$f(\phi)$ and an interfacial contribution. This formulation allows for the modeling of 
interfacial tension and the spontaneous formation of bicontinuous domains characteristic of spinodal decomposition.
To capture not only the diffusive separation of phases but also the resulting fluid motion, the Cahn-Hilliard equation is coupled with the Navier-Stokes equations, leading to the 
Cahn-Hilliard-Navier-Stokes (CHNS) framework. This coupling is essential in systems like bijels, where advection play a significant role in domain coarsening and morphology arrest. 
The momentum conservation equation in this framework is given by,

@@

\begin{equation}
    f_{i}^{eq}(\rho, \vec{u}) = w_i\rho(1 + \frac{\mathbf{c_i} \cdot \mathbf{u}}{c_s^2} + \frac{ \vec{u}(c_{i,\alpha}c_{i,\beta}-c_s^2\mathbb{I}) }{2c_s^4})
    % \frac{(\mathbf{c_i} \cdot \mathbf{u})^2}{2c_s^4} + \frac{\mathbf{u} \cdot \mathbf{u}}{2c_s^2})
    \label{eq:LBM_Feq}
\end{equation}

@@

The momentum flux tensor is calculated from the Chapman-Enskog expansion of \ref{eq:LBM_BGK} to the first order yielding,

\begin{equation}
    \begin{split}
        \rho\frac{\partial \vec{v}}{\partial t} + \nabla \cdot \Pi &= 0 \\
        \Pi_{\alpha \beta} &= \sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta (f_i^{eq} + (1 - \frac{1}{2 \tau})f_i^1)
    \end{split}
\end{equation}

@@

\begin{equation}
    \begin{split}
        \Pi^{(0)}_{\alpha \beta} &= \sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = p \delta_{\alpha \beta} + \rho \vec{u}_\alpha \vec{u}_\beta \\
        \Pi^{(1)}_{\alpha \beta} &= (1 - \frac{1}{2 \tau})\sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = \nu (\nabla_{\alpha}(\rho \vec{\beta}) + \nabla_{\beta}(\rho \vec{\alpha}))
    \end{split}
\end{equation}

With $p = \rho c_s^2$ and $\delta_{\alpha \beta}$ the kronecker delta.

@@

\begin{equation}
    \mathbf{U_{ij}} = \frac{\mu_0 \vec{m}_i \vec{m}_j}{4\pi |r_{ij}|^{3}} \left[ \vec{o}_i \cdot \vec{o}_j - 
    3(\vec{o}_i \cdot \vec{r}_{ij})(\vec{o}_j \cdot \vec{r}_{ij}) \right]
    \label{eq:magnet_potential}
\end{equation}

@@

\begin{equation}
    \mathbf{F}_{ij} = \frac{3 \mu_0}{4 \pi} [\frac{5(\vec{m}_i \cdot \vec{r}_{ij} )(\vec{m}_j
    \cdot \vec{r}_{ij})}{|\vec{r}_{ij}|^7}\vec{r}_{ij} - \frac{(\vec{m}_{i} \cdot \vec{m}_{j})\vec{r}_{ij} + 
    (\vec{m}_{i} \cdot \vec{r}_{ij})\vec{m}_{i} + (\vec{m}_{j} \cdot \vec{r}_{ij})\vec{m}_{j} }{|\vec{r}_{ij}|^5}]
\label{eq:dipole_magnetic_force}
\end{equation}

\begin{equation}
    \mathbf{T}_{ij} = \frac{\mu_0}{4 \pi}[ \frac{3(\vec{m}_{j} \cdot \vec{r}_{ij})m_i \times \vec{r}_{ij} }
    {|\vec{r}_{ij}|^5} - \frac{\vec{m}_{i} \cdot \vec{m}_{j} }{|\vec{r}_{ij}|^3} ]
    \label{eq:dipole_magnetic_torque}
\end{equation}

@@

\begin{equation}
    \mathbf{F_{j}} = \vec{m}_{j}(\vec{o}_{j} \cdot \nabla \vec{B}_{i})
    \label{eq:magnet_force}
\end{equation}

\begin{equation}
    \mathbf{\tau_j} = \vec{m}_{j}(\vec{o}_{j} \times \vec{B}_{i})
    \label{eq:magnet_torque}
\end{equation}

@@

\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c c c c c c c c c||} 
 \hline
 $t_{sim}$ & $L_x$ & $\rho_f$ & $\tau$ & $\eta_f$ & $g_{cc'}$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p$ & $d_c$ & $K_H$ \\ [0.5ex] 
 \hline\hline
 $10^5$ & 256 & 0.7 & 1 & 0.117 & 0.08 & 0.0267 & 0.5 & 1 & 0.15 & 2000$\pi$ & 2/3 & 100\\ [1ex] 
 \hline
\end{tabular}
\caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
\label{table:model_params}
\end{table}

>>>>

Bijels require a multiphysics modeling approach to accurately capture the rich array of physical phenomena 
occurring across multiple length and time scales. Within a bijel, one must consider fluid flow, phase separation, particle-fluid coupling, and interparticle 
interactions. The length scales of interest range in the hundreds of nanometer to  tens of micron scale, demanding a model capable of resolving fine structural details while also 
capturing mesoscale dynamics. In the following sections, a comprehensive review of the relevant physical processes is provided, laying the foundation for the 
numerical methods used in this work.

@@

where $\rho$ is the fluid density and $\vec{u}$ is the fluid velocity. Based on the system being modeled, we assume that the fluid is incompressible, reducing the continuity equation to
$\nabla\cdot \vec{u} = 0$ The momentum conservation equation can also be written by applying Newton's second law to the fluid element. This yields the Cauchy momentum equation, 
where changes in momentum arise due to pressure gradients, viscous stresses, and body forces. The general form of the momentum equation is given by,

% \begin{equation}
    % \rho \left(\frac{\partial u_i}{\partial t} + (u_i\cdot\frac{\partial u_i}{x_i}) \right) = \frac{\partial \sigma_{ij}}{\partial x_j} + f_i
% \end{equation}

\begin{equation}
    \rho \left( \frac{\partial \vec{u}}{\partial t} + (\vec{u}\cdot \nabla \vec{u})  \right) = \nabla \cdot \sigma + \vec{f}
\end{equation}

where $\vec{f}$ is the force exerted on the fluid from external forces such as gravity or magnetic interactions and $\sigma$ is the stress tensor. For a Newtonian, isotropic fluid, 
the viscous stress tensor is given by

% \begin{equation}
%     \sigma_{ij} = -p\delta_{ij} + \eta((\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i}) - \frac{2}{3}(\frac{\partial u_j}{\partial x_i})^2\delta_{ij})
% \end{equation}

\begin{equation}
    \sigma = -p\mathbb{I} + \eta\left( \nabla \vec{u} + (\nabla \vec{u})^T -\frac{2}{3}(\nabla \vec{u})\mathbb{I} \right)
\end{equation}

@@

@@

\begin{equation}
    \bar{l} = \frac{l}{l_0}, \quad \bar{t} = \frac{t}{t_0}, \quad \bar{\rho} = \frac{\rho}{\rho_0}, \quad \bar{\vec{u}} = \frac{\bar{l}}{\bar{t}}, 
\end{equation}

@@

\begin{equation}
    \frac{\partial \bar{\vec{u}}}{\partial \bar{t}} + (\bar{\vec{u}} \cdot\nabla)\bar{\vec{u}} = \frac{1}{Re} \nabla^2 \bar{p} = \frac{p}{\rho \vec{u}^2} - \nabla\bar{p}
\end{equation}

@@

Bijels form through spinodal decomposition of two partially miscible fluids, a process that can be effectively modeled using the Cahn-Hilliard equation. \cite{cahn_spinodal_1961} While the
original equation is written for a concentration of species $c$. For a binary mixture, it can be recast in terms of a conserved scalar order parameter $\phi$, typically representing the 
local concentration difference between the two fluid components. As we are also accounting for the effect of hydrodynamics on the flow of mass, the advection term
from the mass flux $\vec{J}$ cannot be set to 0. Therefore the Cahn-Hilliard equation is given by,

\begin{equation}
    \begin{split}
        \nabla \cdot \vec{J} &= \nabla \cdot \vec{u} - M \nabla \mu \\
        \frac{\partial \phi}{\partial t} + \nabla \cdot \vec{J} &= 0 \\
        \frac{\partial \phi}{\partial t} + \nabla \cdot \phi \vec{u} &= \nabla \cdot \left( M \nabla \mu \right)
    \end{split}
\end{equation}

Here, $M$ is the mobility coefficient and $\mu$ is the chemical potential, which is derived from the variation of the free energy functional $F[\phi]$ which is the sum of a bulk free energy
$f(\phi)$ and an interfacial contribution. This formulation allows for the modeling of interfacial tension and the spontaneous formation of bicontinuous domains characteristic of spinodal decomposition.
To capture not only the diffusive separation of phases but also the resulting fluid motion, the Cahn-Hilliard equation is coupled with the Navier-Stokes equation. This is done
through the pressure which is expressed as the sum of the mechanical $p$ and chemical pressure $p_{chem}$ contributions to yield $p_{tot} = p + p_{chem}$. For a binary system, $p_{chem}$ 
can be written as a function of $\phi$ given by,

\begin{equation}
    p_{chem} = \left[ \phi \mu - f(\phi) - \kappa(\phi \nabla^2 \phi + \frac{1}{2}|\nabla \phi |^2 )\right] \mathbb{I} + \kappa \nabla \phi \otimes \nabla \phi
\end{equation}

The divergence of the above expression is found to be $\nabla \cdot p_{chem} = -\phi \nabla \mu$. Substituting the $p_{tot}$ for $p$ in the Navier Stokes equation,
the Cahn-Hilliard-Navier-Stokes (CHNS) framework is obtained. This coupling is essential in systems like bijels, where advection play a significant role in domain 
coarsening and morphology arrest. The momentum conservation equation in this framework is given by,

@@

\begin{equation}
    f_i^{\text{eq}}(\rho, \vec{u}) = w_i \rho \left( 1 + \frac{\vec{c}_i \cdot \vec{u}}{c_s^2} + \frac{(\vec{c}_i \otimes \vec{c}_i - c_s^2 \mathbb{I}) : (\vec{u} \otimes \vec{u})}{2c_s^4} \right)
    \label{eq:LBM_Feq}
\end{equation}

@@

The momentum flux tensor is calculated from the Chapman-Enskog expansion of \ref{eq:LBM_BGK} to the second order yielding,

\begin{equation}
    \begin{split}
        \rho\frac{\partial \vec{u}}{\partial t} + \nabla \cdot \Pi &= 0 \\
    \end{split}
\end{equation}

@@

\begin{equation}
    \begin{split}
        % \Pi^{(0)}_{\alpha \beta} &= \sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = p \delta_{\alpha \beta} + \rho \vec{u}_\alpha \vec{u}_\beta \\
        % \Pi^{(1)}_{\alpha \beta} &= (1 - \frac{1}{2 \tau})\sum_i \mathbf{c_i}_\alpha \mathbf{c_i}_\beta f_i^{eq} = \nu (\nabla_{\alpha}(\rho \vec{\beta}) + \nabla_{\beta}(\rho \vec{\alpha}))
        \Pi^{(0)} &= \sum_i f_i^{eq} \vec{c}_i \otimes \vec{c}_i = p\mathbb{I} + \rho \vec{u} \otimes \vec{u} \\
        \Pi^{(1)} &= (1 - \frac{1}{2 \tau})\sum_i f_i^{neq} \vec{c}_i \otimes \vec{c}_i = -\eta (\nabla \vec{u} + (\nabla \vec{u})^T)
    \end{split}
\end{equation}

With $p = \rho c_s^2$.

@@

\begin{equation}
    U_{ij} = \frac{\mu_0 \vec{m}_i \vec{m}_j}{4\pi |r_{ij}|^{3}} \left[ \vec{o}_i \cdot \vec{o}_j - 
    3(\vec{o}_i \cdot \vec{r}_{ij})(\vec{o}_j \cdot \vec{r}_{ij}) \right]
    \label{eq:magnet_potential}
\end{equation}

@@

\begin{equation}
    \vec{F}_{ij} = \frac{3 \mu_0}{4 \pi} [\frac{5(\vec{m}_i \cdot \vec{r}_{ij} )(\vec{m}_j
    \cdot \vec{r}_{ij})}{|\vec{r}_{ij}|^7}\vec{r}_{ij} - \frac{(\vec{m}_{i} \cdot \vec{m}_{j})\vec{r}_{ij} + 
    (\vec{m}_{i} \cdot \vec{r}_{ij})\vec{m}_{i} + (\vec{m}_{j} \cdot \vec{r}_{ij})\vec{m}_{j} }{|\vec{r}_{ij}|^5}]
\label{eq:dipole_magnetic_force}
\end{equation}

\begin{equation}
    \vec{T}_{ij} = \frac{\mu_0}{4 \pi}[ \frac{3(\vec{m}_{j} \cdot \vec{r}_{ij})m_i \times \vec{r}_{ij} }
    {|\vec{r}_{ij}|^5} - \frac{\vec{m}_{i} \cdot \vec{m}_{j} }{|\vec{r}_{ij}|^3} ]
    \label{eq:dipole_magnetic_torque}
\end{equation}

@@

\begin{equation}
    \vec{F}_{j} = \vec{m}_{j}(\vec{o}_{j} \cdot \nabla \vec{B}_{i})
    \label{eq:magnet_force}
\end{equation}

\begin{equation}
    \vec{T}_{j} = \vec{m}_{j}(\vec{o}_{j} \times \vec{B}_{i})
    \label{eq:magnet_torque}
\end{equation}

@@

\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c c c c c c c c c||} 
 \hline
 $t_{sim}$ & $L_x$ & $\rho_f $ & $\tau$ & $\eta_f $ & $g_{cc'} \Delta m(\Delta t)^2/(\Delta x)^5$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p (\Delta x)^3$ & $d_c \Delta x$ & $K_H$ \\ [0.5ex] 
 \hline\hline
 $10^5 \Delta t$ & 256$\Delta x$ & 0.7 $\frac{\Delta m}{(\Delta x)^3}$ & 1$\Delta t$ & 0.117 $\frac{\Delta m}{\Delta x \Delta t}$ & 0.08 & 0.0267 $\frac{\Delta m}{(\Delta t)^2}$ & 0.5 & 1 $\frac{\Delta m}{(\Delta x)^3}$ & 0.15 & 2000$\pi (\Delta x)^3$ & 2/3 $\Delta x$& 100 $(\Delta x)^{1/2}(\Delta t)^2/\Delta m$\\ [1ex] 
 \hline
\end{tabular}
\caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
\label{table:model_params}
\end{table}

### 2025-04-15 chapters/lit_review_new.tex
Making notation consistent

The thermodynamic equilibrium of a binary fluid mixture can be described by its Gibbs free energy, given as $G = \Delta H - T \Delta S$, where \(\Delta H\) is the enthalpy change, 
\(T\) is temperature, and \(\Delta S\) is the entropy change. The onset of phase separation occurs at the binodal line, defined where \(\frac{dG}{dx} = 0\), with \(x\) representing the composition. 
Although the system is metastable, it remains uniform until fluctuations give rise to small nuclei. The free energy of each nucleus reflects a 
balance between the bulk free energy gain from phase separation and the interfacial energy penalty, expressed as \(\Delta G = \frac{4}{3}\pi r^3 \Delta g_v + 4 \pi r^2 \sigma\), where \(r\) is 
the nucleus radius, \(\Delta g_v\) is the free energy change per unit volume, and \(\sigma\) is the interfacial tension \cite{thanh_mechanisms_2014}. 
Nuclei that exceed the critical radius \(r_c = \frac{2\sigma}{|\Delta g_v|}\) will grow, driving the system toward phase separation via nucleation and growth \cite{thanh_mechanisms_2014}. 
This transformation process is commonly modeled by the Avrami equation, \(Y = 1 - \exp(-K t^n)\), where \(Y\) is the 
transformed fraction, \(K\) is a rate constant incorporating nucleation and growth kinetics, and \(n\) is the Avrami exponent, which reflects the dimensionality and mechanism of the transformation
\cite{avrami_kinetics_1939}.

At the binodal, the system is still metastable, meaning that unless perturbations are introduced to form nuclei, the mixture remains homogeneous \cite{thanh_mechanisms_2014}.
However, a deeper quench into the two-phase region leads to the spinodal line, defined by the stability criterion \(\frac{d^2G}{dx^2} = 0\) \cite{cahn_free_1958}. 
Within this region, the system is unstable to even infinitesimal composition fluctuations, and phase 
separation proceeds spontaneously without the need for nucleation. This process, known as spinodal decomposition, is characterized by the continuous and simultaneous growth of interconnected 
domains of both phases \cite{cahn_free_1958}. Unlike nucleation and growth, which relies on localized events, spinodal decomposition 
results in a bicontinuous structure driven by the system's attempt to minimize 
free energy through composition modulation \cite{cahn_free_1958}. The dynamics of spinodal decomposition were characterized by Cahn and Hilliard \cite{cahn_spinodal_1961}. 
We first begin by defining the free energy of a regular binary solution given by,

@@

The most important difference between these two phase separation methods is the morphology of the phase separated structure. While nucleation and growth generates discontinuous droplets,
spinodal decomposition creates continuous domains that have tunable domain sizes and tortuosity which are attractive in many materials applications such as battery electrodes, filtration
membranes and catalyst supports.

>>>>

The thermodynamic equilibrium of a binary fluid mixture can be described by its Gibbs free energy, given as $\Delta G = \Delta H - T \Delta S$, where \(\Delta H\) is the enthalpy change, 
\(T\) is temperature, and \(\Delta S\) is the entropy change. The onset of phase separation occurs at the binodal line, defined where \(\frac{dG}{dx} = 0\), with \(x\) representing the composition. 
Although the system is metastable, it remains uniform until fluctuations give rise to small nuclei. The free energy of each nucleus reflects a 
balance between the bulk free energy gain from phase separation and the interfacial energy penalty, expressed as \(\Delta G = \frac{4}{3}\pi r^3 \Delta g_v + 4 \pi r^2 \sigma\), where \(r\) is 
the nucleus radius, \(\Delta g_v\) is the free energy change per unit volume, and \(\sigma\) is the interfacial tension \cite{thanh_mechanisms_2014}. 
Nuclei that exceed the critical radius \(r_c = \frac{2\sigma}{|\Delta g_v|}\) will grow, driving the system toward phase separation via nucleation and growth \cite{thanh_mechanisms_2014}. 
This transformation process is commonly modeled by the Avrami equation, \(Y = 1 - \exp(-K t^n)\), where \(Y\) is the 
transformed fraction, \(K\) is a rate constant incorporating nucleation and growth kinetics, and \(n\) is the Avrami exponent, which reflects the dimensionality and mechanism of the transformation
\cite{avrami_kinetics_1939}.

At the binodal, the system is still metastable, meaning that unless perturbations are introduced to form nuclei, the mixture remains homogeneous \cite{thanh_mechanisms_2014}.
However, a deeper quench into the two-phase region leads to the spinodal line, defined by the stability criterion \(\frac{d^2G}{dx^2} = 0\) \cite{cahn_free_1958}. 
Within this region, the system is unstable to even infinitesimal composition fluctuations, and phase 
separation proceeds spontaneously without the need for nucleation. This process, known as spinodal decomposition, is characterized by the continuous and simultaneous growth of interconnected 
domains of both phases \cite{cahn_free_1958}. Unlike nucleation and growth, which relies on localized events, spinodal decomposition 
results in a bicontinuous structure driven by the system's attempt to minimize 
free energy through composition modulation \cite{cahn_free_1958}. The dynamics of spinodal decomposition were characterized by Cahn \cite{cahn_spinodal_1961}. 
We first begin by defining the free energy of a regular binary solution given by,

@@

The most important difference between these two phase separation methods is the morphology of the phase separated structure. While nucleation and growth generates discontinuous droplets,
spinodal decomposition creates continuous domains which are attractive in many materials applications such as battery electrodes, filtration membranes and catalyst supports.

### 2025-04-15 chapters/model_params.tex
Making notation consistent

\begin{table}[h!]
\centering
\begin{tabular}{||c c c c c c c c c c c c c||} 
 \hline
 $t_{sim}$ & $L_x$ & $\rho_f$ & $\tau$ & $\eta_f$ & $g_{cc'}$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p$ & $d_c$ & $K_H$ \\ [0.5ex] 
 \hline\hline
 $10^5$ & 256 & 0.7 & 1 & 0.117 & 0.08 & 0.0267 & 0.5 & 1 & 0.15 & 2000$\pi$ & 2/3 & 100\\ [1ex] 
 \hline
\end{tabular}
\caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
\label{table:model_params}
\end{table}

In these simulations, the aspect ratio is defined as $\alpha = \frac{R_{\parallel}}{R_{\perp}}$ with $\alpha = 0.5, 1, 2$ 
used in these simulations. All particle geometries are volume matched, based on the spherical particle volume. For the 
spherical particle, the radius was set at $R_{\parallel} = R_{\perp} = 7.9$ which sets the $\alpha = 0.5$ particles to 
$R_{\parallel} = 5, R_{\perp} = 10$ and the $\alpha = 2$ particles to $R_{\parallel} = 12.6, R_{\perp} = 6.3$. 
$R_{\parallel}$ and $R_{\perp}$ is the radius of the particle parallel and perpendicular to the symmetry axis of 
the particle respectively. These values are identical to what was used in Gunther et al, allowing comparisons to the 
trends they observed. \cite{gunther_timescales_2014} The particles were randomly placed in the system and an equilibration
step was performed to push the particles further away from each after placement. Once equilibration is performed, a 
constant magnetic field is switched on with dimensionless strengths defined using $\bar{B}$.

@@

Bijel templates have been synthesized using water/2-6-lutidine for further applications. \cite{lee_making_2013} 
While intrinsically polymerizable bijels have been prepared using oligomeric polymers, STRIPS and VIPS currently 
utilize small molecule liquids in their bijel casting mixtures. Therefore, an experimentally viable system using 
water/2-6-lutidine will be discussed in the context of the work presented here. The critical temperature (UCST) 
for this system is $T_c = 34 ^{\circ}C$, with many systems heated to $T = 40^{\circ}C$ to form the bijel. At this 
temperature, the fluid properties are $\sigma = 0.22 mN/m$ and $\eta = 2.38 mPas$. \cite{grattoni_lower_1993} 
Fei et al. developed a method to synthesize polystyrene microparticles ($(R_p = 2 \mu m)$) with tunable geometries 
by mechanically stretching or compressing them, then coating them with nickel to create magnetic microparticles with 
a dipole moment of approximately$\approx 3 \cdot 10^{-14} Am^2$. \cite{fei_active_2017, fei_magneto-capillary_2020} 
Comparing the physical properties to simulation parameters, the simulations correspond to a length scale of
$\Delta x = 252 \cdot 10^{-9} \text{m}$, timescale of $\Delta t = 624 \cdot 10^{-9} \text{s}$, 
mass scale of $\Delta m = 2.24 \cdot 10^{-15} \text{kg}$ and charge scale of $\Delta q = 2.948 \cdot 10^{-7} \text{C}$.

>>>>

% \begin{table}[h!]
% \centering
% \begin{tabular}{||c c c c c c c c c c c c c||} 
%  \hline
%  $t_{sim}$ & $L_x$ & $\rho_f$ & $\tau$ & $\eta_f$ & $g_{cc'}$ & $\sigma$ & $\phi_f$ & $\rho_p$ & $\phi_p$ & $V_p$ & $d_c$ & $K_H$ \\ [0.5ex] 
%  \hline\hline
%  $10^5$ & 256 & 0.7 & 1 & 0.117 & 0.08 & 0.0267 & 0.5 & 1 & 0.15 & 2000$\pi$ & 2/3 & 100\\ [1ex] 
%  \hline
% \end{tabular}
% \caption{Summary of the fluid, particle and model parameters used in the proposed simulations}
% \label{table:model_params}
% \end{table}

\begin{table}
    \centering
    \caption{Summary of the parameters corresponding to the fluid, particle and model used in the simulations}
    \label{table:model_params}
    \begin{tabular}{|c|r|}
    \hline
    % Parameter & Value \\
    % \hline
    $L_V/\Delta x$ & 256 \\
    $\rho \cdot (\Delta x)^3/\Delta m$ & 0.7 \\
    $\nu \cdot \Delta t/(\Delta x)^2$ & 1/6 \\
    $\sigma \cdot (\Delta t)^2/\Delta m$ & 0.0267 \\
    $\tau/\Delta t$ & 1 \\
    $g \cdot \Delta m(\Delta t)^2/(\Delta x)^5$ & 0.08 \\
    $\phi_f$ & 0.5 \\
    $\phi_p$ & 0.15 \\
    $n_p$ & 1200 \\
    $\rho_p \cdot (\Delta x)^3/\Delta m$ & 1 \\
    $V_p/(\Delta x)^3$ & $2000\pi/3$ \\
    $m/(\Delta i(\Delta x)^2)$ & 1 \\
    $d_c/\Delta x$ & 2/3 \\
    $K_H\cdot (\Delta x)^{1/2}(\Delta t)^2/\Delta m$ & 100 \\
    \hline
    \end{tabular}
\end{table}

In these simulations, the aspect ratio is defined as $\alpha = \frac{R_{\parallel}}{R_{\perp}}$ with $\alpha = 0.5, 1, 2$ 
used in these simulations. All particle geometries are volume matched, based on the spherical particle volume. For the 
spherical particle, the radius was set at $R_{\parallel} = R_{\perp} = 7.9 \Delta x$ which sets the $\alpha = 0.5$ particles to 
$R_{\parallel} = 5 \Delta x, R_{\perp} = 10 \Delta x$ and the $\alpha = 2$ particles to $R_{\parallel} = 12.6, R_{\perp} = 6.3 \Delta x$. 
$R_{\parallel}$ and $R_{\perp}$ is the radius of the particle parallel and perpendicular to the symmetry axis of 
the particle respectively. These values are identical to what was used in Gunther et al, allowing comparisons to the 
trends they observed. \cite{gunther_timescales_2014} The particles were randomly placed in the system and an equilibration
step was performed to push the particles further away from each after placement. Once equilibration is performed, a 
constant magnetic field is switched on with dimensionless strengths defined using $\bar{B}$.

@@

Bijel templates have been synthesized using water/2-6-lutidine for further applications. \cite{lee_making_2013} 
While intrinsically polymerizable bijels have been prepared using oligomeric polymers, STRIPS and VIPS currently 
utilize small molecule liquids in their bijel casting mixtures. Therefore, an experimentally viable system using 
water/2-6-lutidine will be discussed in the context of the work presented here. The critical temperature (UCST) 
for this system is $T_c = 34 ^{\circ}\text{C}$, with many systems heated to $T = 40^{\circ}\text{C}$ to form the bijel. At this 
temperature, the fluid properties are $\sigma = 0.22 \text{mN/m}$ and $\eta = 2.38 \text{mPas}$. \cite{grattoni_lower_1993} 
Fei et al. developed a method to synthesize polystyrene microparticles ($(R_p = 2 \text{\mu m})$) with tunable geometries 
by mechanically stretching or compressing them, then coating them with nickel to create magnetic microparticles with 
a dipole moment of approximately$\approx 3 \cdot 10^{-14} \text{Am^2}$. \cite{fei_active_2017, fei_magneto-capillary_2020} 
Comparing the physical properties to simulation parameters, the simulations correspond to a length scale of
$\Delta x = 252 \cdot 10^{-9} \text{m}$, timescale of $\Delta t = 624 \cdot 10^{-9} \text{s}$, 
mass scale of $\Delta m = 2.24 \cdot 10^{-15} \text{kg}$ and charge scale of $\Delta q = 2.948 \cdot 10^{-7} \text{C}$.

### 2025-04-15 chapters/paper1_5.tex
Making notation consistent

\section[Introduction]{Introduction\protect\footnote{This section is based on work submited to the American Institude of Physics, Physics of Fluids journal.
                        It is reproduced from submission number \#POF25-AR-DSFD2024-03180, with the permission of AIP Publishing.}}

>>>>

\section[Introduction]{Introduction\protect\footnote{This chapter is based on work submited to the American Institude of Physics, Physics of Fluids journal.
                        It is reproduced from submission number \#POF25-AR-DSFD2024-03180, with the permission of AIP Publishing.}}
